---
title: "LTM Distribution"
author: "Joseph Roy"
date: "2022-12-20"
output: html_document
---
#language       R                                
#version.string R version 4.2.0 (2022-04-22 ucrt)
#nickname       Vigorous Calisthenics 


### Getting data for Lion tailed Macaque distribution data from GBIF- Global Biodiversity Information Facility


```{r}
library(rgbif) #global biodiversity information framework
library(mapview) #plotting spatial data 
#library(scrubr) #clean spatial data- discontuiued
library(sp) #convert spatial data to spatial object 
library(dplyr) 
```
- Making a key for species- Macaca silenus
```{r}
key <- name_suggest(q='Macaca silenus', 
                    rank='species')$data$key[1]
```

- using occ_search from gbif package just to see the count of observations

```{r}
occ_search(taxonKey=key, limit=0)$meta$count
```
- now actual search using the key, used limit to limit the maximum number of observation to 200

```{r}
spdat.test <- occ_search(taxonKey = key, 
                         return = "data", limit = 200)
```

- extracting data from the whole
```{r}
spdat.test <- spdat.test$data
```

- removing values other than from India

```{r}
spdat.test1 <- subset(spdat.test, 
                  country == "India")
```

- sub-setting lat long and species using dplyr command select
```{r}
dat.test <- select(spdat.test1, 
                   decimalLongitude, decimalLatitude, species)
```

- renaming columns 
```{r}
colnames(dat.test) <- c("longitude", "latitude", "species")
```

- removing NAs
```{r}
dat.test <- na.omit(dat.test)
```

these line is from scruber which is now discontinued
need to find something like that which could work
used to clean the gps data 
dat.test<-dframe(dat.test) %>% coord_impossible()
dat.test<-dframe(dat.test) %>% coord_unlikely()


- converting the lat long to spatial points
proj4string = CRS("+init=epsg:4326") is the fromat of the data 
```{r}
sp.test <- SpatialPoints(coords = cbind(dat.test$longitude, dat.test$latitude),
                         proj4string = CRS("+init=epsg:4326"))
```

- adding secies to spatial points (sp package)
```{r}
sp.test$species <- dat.test$species
```

- using mapview to plot the points
```{r echo=FALSE}
mapview(sp.test, color="green")
```


- let's save the spdat.test data as a csv file 
- In case we want to use it later without having to re-download them all!

```{r}
write.csv(spdat.test, "GBIF_data.csv")

?mapview
```



